A new method to estimate dark matter halo concentrations

### 2015-08-21 paper/article.tex
revised abstract

\author{Christian Poveda, Jaime E. Forero-Romero}
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{cn.poveda542@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}

@@

We present a new method to estimate the concentration of dark matter
halos in N-body simulations.
Our method is based on a fit to the integrated mass as a function of
halo radius.
The main advantage of this method is that it uses the full particle information
without any binning.
We test our method both on mock and N-body halos to compare it against
two popular methods to find concentrations: maximum radial velocity
measurements and radial particle binning to estimate the density.
Tests on the mock halos show that the accuracy of our method to
recover input concentrations can achieve $0.1\%$ while for the maximum
radial velocity and density methods it is on the order of $0.5\%$ and
$40\%$ respectively.
We also measure the mass-concentration relationship on the N-body
data.
With respect to the other two approaches our method produces a
flatter relationship, while its normalization falls below the maximum
velocity method and above the density method.
\end{abstract}

>>>>

\author{Christian Poveda, Jaime E. Forero-Romero}
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{cn.poveda542@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}
\author{Juan Carlos Mu\~noz-Cuartas}
\affil{UdeA, Medell\'in, Colombia}
\email{xxx@udea.edu.co}

@@

We present a new method to estimate the concentration of dark matter
halos in N-body simulations.
Our method is based on a fit to the integrated mass profile as a function of
halo radius.
The main advantage of this method is that it uses the full particle information
without any binning.
We test our method both on mock and N-body halos to compare it against
two popular methods to find concentrations: maximum radial velocity
measurements and radial particle binning to estimate the density.
Tests on the mock halos show that the accuracy of our method to
recover input concentrations varies with the number of particles in
the halo. For halos sampled with $20$ particles our method recovers
the input concentration with $10\%$ accuracy, while for the maximum
radial velocity and density methods the accuracy is on the order of $20\%$ and
$100\%$, respectively. For halos samples with $10^4$ particles our
method achieves an accuracy of $0.01\%$ while the velocity and density
methods achieve $0.1\%$ and $1\%$ accuracy, respectively.
We also measure the mass-concentration relationship on the N-body
data.
With respect to the other two approaches our method produces a
flatter relationship, while its normalization falls below the maximum
velocity method and above the density method.
\end{abstract}
